Think deep for reef resilience

### 2025-07-02 paper/paper_draft.qmd
Add justification on spearmans correlation

>>>>

The distribution of number of years above carbonate-cover thresholds is right-skewed, with many reefs experiencing low numbers of years above thresholds. Similarly, reef median depth levels and log (natural) total connectivity strength levels follow right-skewed distributions. Therefore, we analyse the correlation between number of years above carbonate-cover thresholds and these characteristics using Spearman's correlation coefficient.
